Differential invariant signatures for planar Lie group transformations of images

### 2020-11-12 paper/newpaper.tex
minor

For image recognition it is then natural to seek representations of objects that do not change as these various transformation groups act. If the space of objects is denoted $M$ and the appearance transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$. One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{}). Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will place all of the shapes into the reference frame of one template example. However, analysis on these quotient spaces is rarely simple~\cite{}, and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit. An alternative option is to seek $\mathcal{G}$-invariant functions on $M$, which is what we consider here. In this case, rather than considering the image of the object, one works with an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group. This reduces the recognition problem to recognising higher-dimensional invariant signatures.

Something about signatures
3. The signature must vary continuously with respect to the image, either for all smooth
images or for all except a set of sufficiently high codimension. This is essential if the
signature is to be used to detect similarity of images, but it fails for the rational
invariants found in the literature.
Invariant signatures -- self-equivalences

@@

However, of particular saliance for object recognition in scenes is the need to be robust to occlusions, where one object obscures some part of another. This leads one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology. This is sufficient to compute, e.g., derivatives of an object. 
Olver et al. joint differential invars (aka semi-diff)
MOMENTS

@@

We consider a wide range of planar groups, both finite-dimensional Lie groups and infinite-dimensional pseudo-Lie ones; as we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups.

@@

In this paper we provide a tutorial on differential invariants for planar Lie groups (e.g.
Euclidean, affine, projective) since they are relatively simple, useful,
and relevant to images. We'll use these to demonstrate the methods of
constructing and using differential invariant signatures.

@@

The question of how to compare invariant signatures is not considered further in this paper.

@@

%Groups we've done:

%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff

@@

\todo[inline]{visual obstruction}

\section{Differential invariants of E(2) through tensor contraction}
While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$. In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance as they are equivalent. We therefore use subscript indices exclusively.

@@

@@

\section{Use in practice; noise, singularities}
 \todo[inline]{Experimental}

Some calculation detail

\todo[inline]{Signature examples}
\todo[inline]{Alien: Smoothing, noise}
\todo[inline]{Spot the group?}

@@

\todo[inline]{Number of derivatives}
\todo[inline]{Noise; integral invariants, Fourier}
\todo[inline]{Is there a general theory - syzygy??}

>>>>

For image recognition it is then natural to seek representations of objects that do not change as these various transformation groups act. If the space of objects is denoted $M$ and the appearance transformations form a group $\mathcal{G}$, then mathematically one seeks a way to study objects in $M / \mathcal{G}$. One way to achieve this is by transforming all objects to match a chosen target object by registration (the transformation of the appearance of one shape to match another, typically by gradient descent on a matching function, see e.g.~\cite{}). Hence for the group of similarity transformations (rotation and reflection, translation, and scale), a Procrustes alignment~\cite{} will place all of the shapes into the reference frame of one template example. However, analysis on these quotient spaces is rarely simple~\cite{}, and if one is interested in the object, and not the transformation, then it necessitates a lot of computational work for relatively little benefit.

An alternative option is to seek $\mathcal{G}$-invariant functions on $M$, which is what we consider here. In this case, rather than considering the image of the object, one works with an invariant signature of some kind, which represents the object modulo the action of elements from the relevant group. These signatures are typically of a higher dimensionality that the original image.

@@

Olver et al. joint differential invars (aka semi-diff)
MOMENTS

In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another. These constraints lead to the 
This leads one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology. This is sufficient to compute, e.g., derivatives of an object. 
This fails for a variety of 
However, of particular saliance for object recognition in scenes is the need to be robust to occlusions,

The introduction of an invariant signature reduces the recognition problem to one of comparing the higher-dimensional signatures that encode the desired self-equivalences. In this paper we introduce the mathematical considerations necessary to construct invariant signatures to the planar Lie groups that can transform 2D images. We consider a wide range of planar groups, both finite-dimensional Lie groups and infinite-dimensional pseudo-Lie ones; as we shall show, the lattice structure of the set of groups influences the relationship between the sets of invariants for the different groups. We provide sample signature sets for the various groups we consider, and examples of the appearance of those signatures for transformations of a simple, smooth image, but do not consider the question of a complete practical implementation. We do not consider the matching of the signatures, for which several methods already exist, such as~\cite{}.

This is essential if the
signature is to be used to detect similarity of images, but it fails for the rational
invariants found in the literature.

@@

@@

@@

@@

%Groups we've done:
%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff

@@

\section{Differential invariants through tensor contraction}
While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$. In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance as they are equivalent. We therefore use subscript indices exclusively.

@@

\todo[Move this one out]

@@

@@

\todo[inline]{Number of derivatives}
\todo[inline]{Noise; integral invariants, Fourier}
\todo[inline]{Is there a general theory - syzygy??}
\todo[inline]{Difficulties of a practical implementation}
